Clustering exploration for `r params$sample_id`

### 2024-09-05 analyses/cell-type-wilms-tumor-06/notebook_template/03_clustering_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook_template/03_clustering_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

```{r fig.width=8, fig.height=2.5, out.width='100%'}
for(feature in CellType_metadata$ENSEMBL_ID[CellType_metadata$ENSEMBL_ID %in% rownames(srat@assays$SCT)]){
 tryCatch(
  expr =  {
    tmp <-  visualize_feature(srat, features = feature, group.by = "seurat_clusters")
    print(tmp)
  },
  error = {
    expr= print("feature not found")
    }
 )
}
```

>>>>

```{r fig.width=8, fig.height=2.5, out.width='100%'}
for(feature in CellType_metadata$ENSEMBL_ID[CellType_metadata$ENSEMBL_ID %in% rownames(srat@assays$SCT)]){
   print(visualize_feature(srat, features = feature, group.by = "seurat_clusters"))
}
```
